Lifting CDCL to Numerical Domains

### 2016-09-27 domains.tex
program model

\section{Abstract Domains}
\subsection{Program Models}

\subsection{Interval Abstract Domain}
The {\em Interval} abstract domain is a lattice 
$ItvDom = (ItvElm, \sle_{I}, \join_{I}, \meet_{I})$, where
$ItvElm: (Var \rightarrow Itv) \cup \{\bot\}$, and $Itv$ is 
the set of intervals of type $[l,u]$ over numeric data 
type with $l \leq u$. The least element is $\bot$ and the 
greatest element is $\top$ which maps all variables to their
minimum ($min$) and maximum ($max$) values.  An interval 
$\langle x, [min, v] \rangle$ is written as $x \leq v$.  The 
partial order $\sle_{I}$ over elements in the set $Itv$ is 
given by $I_1 \sle_{I} I_2$ if $I_2$ contains $I_1$.
A join $(\join_{I})$ of two intervals $\langle x_1 \rightarrow [l_1, u_1], 
x_1 \rightarrow [l_2, u_2] \rangle$ is an interval 
$\langle x_1 \rightarrow [min(l_1, l_2), max(u_1, u_2)]$.
A meet $(\meet_{I})$ of two intervals $\langle x_1 \rightarrow [l_1, u_1], 
x_1 \rightarrow [l_2, u_2] \rangle$ is an interval 
$\langle x_1 \rightarrow [max(l_1, l_2), min(u_1, u_2)] \rangle$.
The galois connection between the concrete environment and intervals is 
given as follows.
\[\alpha(x) = \{[inf(x), sup(x)] | x \in Var\} \qquad   \alpha(\emptyset) = \bot \]
\[\gamma[p,q] = \{c \in \mathbb{Z} | p \leq c \leq q\} \qquad \gamma(\bot) = \emptyset \]
For a program with $N$ variables, there are a total of 
$2*N$ intervals. The intervals restrict the set of values 
taken by program variables at each program point, starting 
from $[-\infty, \infty]$.

>>>>

\section{Abstract Domains}
\textbf{Programs:}
%
A {\em program} $\mathcal{P}$ is formally defined as follows.
\[
\begin{array}[t]{@{}lll}
\mathcal{P} & {:}{:}{=} & \mathit{Procedure} \\
\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{function(Var_1,\dots,Var_n)} \\
\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\
\end{array}
\]
Consider sets of expressions $Exp$ and Boolean expressions $BExp$
over variables $Var$ of $\mathcal{P}$.  The variables in $Var$ 
can take numeric values in $Val$.  A procedure is denoted as 
$\mathit{function(Var_1,\dots,Var_n)}$.  A $\mathit{CStatement}$ 
is an assignment, conditional, sequential concatenation or a loop.
\rmcmt{post}
\subsection{Interval Abstract Domain}
The {\em Interval} abstract domain is a lattice 
$ItvDom = (ItvElm, \sle_{I}, \join_{I}, \meet_{I})$, where
$ItvElm: (Var \rightarrow Itv) \cup \{\bot\}$, and $Itv$ is 
the set of intervals of type $[l,u]$ over numeric data 
type with $l \leq u$. The least element is $\bot$ and the 
greatest element is $\top$ which maps all variables to their
minimum ($min$) and maximum ($max$) values.  An interval 
$\langle x, [min, v] \rangle$ is written as $x \leq v$.  The 
partial order $\sle_{I}$ over elements in the set $Itv$ is 
given by $I_1 \sle_{I} I_2$ if $I_2$ contains $I_1$.
A join $(\join_{I})$ of two intervals $\langle x_1 \rightarrow [l_1, u_1], 
x_1 \rightarrow [l_2, u_2] \rangle$ is an interval 
$\langle x_1 \rightarrow [min(l_1, l_2), max(u_1, u_2)]$.
A meet $(\meet_{I})$ of two intervals $\langle x_1 \rightarrow [l_1, u_1], 
x_1 \rightarrow [l_2, u_2] \rangle$ is an interval 
$\langle x_1 \rightarrow [max(l_1, l_2), min(u_1, u_2)] \rangle$.
The galois connection between the concrete environment and intervals is 
given as follows.
\[\alpha(x) = \{[inf(x), sup(x)] | x \in Var\} \qquad   \alpha(\emptyset) = \bot \]
\[\gamma[p,q] = \{c \in \mathbb{Z} | p \leq c \leq q\} \qquad \gamma(\bot) = \emptyset \]
For a program with $N$ variables, there are a total of 
$2*N$ intervals. The intervals restrict the set of values 
taken by program variables at each program point, starting 
from $[-\infty, \infty]$.
